Seagrass mapping and monitoring along the coasts of Crete, Greece

### 2011-01-21 MScDiplom_Lemenkova.tex
added collage of general research approach, Inkscape

\textbf{Software and utilities used in the current work}:\\
\begin{itemize}
	\item \href{http://www.esri.com/software/arcgis/index.html}{ArcGIS 10.0}: mapping, data integration and spatial analysis
	\item \href{http://www.erdas.com/products/ERDASIMAGINE/ERDASIMAGINE/Details.aspx}{Erdas Imagine}: imagery processing and classification
	\item \href{http://www.filewatcher.com/b/ftp/ftp.dfd.dlr.de/pub/WASI.0.0.html}{WASI Water Color Simulator}, for modelling optical water properties under changing environment
	\item \href{http://welcome.hp.com/country/us/en/prodserv/handheld.html}{iPAQ} and GPS for data capture during the fieldwork
	\item \href{http://www.bibtex.org/de/}{BibTeX}, for management of bibliography and reference database
	\item \href{http://www.latex-project.org/}{\LaTeX}, for document typesetting, formatting and performing pdf output
	\item \href{http://www.python.org/}{Python language}, for writing auxiliary scripts (e.g. raw data interpolation)
	\item \href{http://www.gnuplot.info/}{Gnuplot} for plotting graphs
	\item \href{http://www.openoffice.org/}{Open Office} : document typesetting, data preprocessing and preliminary statistical evalution
	\item \href{http://calc2latex.sourceforge.net/}{Calc2LaTeX} : converting spreadsheets into \LaTeX environment
	\item \href{http://www.spss.com/}{SPSS (PASW Statistics 18)} : statistical data edition and analysis 
	\item \href{http://gretl.sourceforge.net/}{Gretl: Gnu Regression, Econometrics and Time-series Library} for statistic analysis
	\item \href{http://staruml.sourceforge.net/en/}{StarUML} , \href{http://live.gnome.org/Dia}{Dia} , \href{http://argouml.tigris.org/}{AgroUML}: diagramming flowcharts for work algorithms
\end{itemize}
\pagebreak

@@

\begin{figure}[h]
	\centering
	\includegraphics[scale=0.48]{UML_ClassDiagram.jpg}
	\caption{General methodological approach for the analysis of spectral signatures. \href{http://argouml.tigris.org/}{AgroUML}}
	\label{fig:16}
\end{figure}

@@

@@

\begin{table}
\rowcolors{1}{Khaki}{LightYellow}
\caption{Statistical analysis of the measurements of spectral reflectance of P.oceanica (fragment).}
\centering
  \begin{tabular}{| c | c | c | c | c |}
    \hline
   	 \textbf{Statistical values} & \textbf{318.19} & \textbf{418.3448} & \textbf{518.8361} & \textbf{619.3662} \\ \hline \hline
	    Mean & 0.034521 & 0.049235 & 0.076088 & 0.085287 \\ \hline
	    St Dev & 0.019849 & 0.030338 & 0.042587 & 0.046569 \\ \hline
	   Median & 0.033035 & 0.046197 & 0.07704 & 0.080277 \\ \hline
	   Q1 & 0.019293 & 0.023706 & 0.045606& 0.049468 \\ \hline
	   Q3 & 0.042477 & 0.057934 & 0.092289 & 0.114191 \\ \hline
	   Minimum & 0.007898 & 0.010087 & 0.021373 & 0.022691 \\ \hline
	   Maximum & 0.076835 & 0.110906 & 0.18938 & 0.216231 \\ \hline
	   25th Pct & 0.019293 & 0.023706 & 0.045606 & 0.049468 \\ \hline
	   50th Pct & 0.013743 & 0.022491 & 0.031435 & 0.030808 \\ \hline
	   75th Pct & 0.009441 & -0.01174 & -0.01525 & -0.03391 \\ \hline
	   Min & 0.011395 & 0.013618 & 0.024232 & 0.026777 \\ \hline
	   Max & 0.034358 & 0.052972 & 0.097091 & 0.1 \\ \hline
  \end{tabular}
   \label{tab:4}
\end{table}

>>>>

\textbf{Software and utilities used in the current work}:\\
\begin{itemize}
	\item \href{http://www.esri.com/software/arcgis/index.html}{ArcGIS 10.0}: mapping, data integration and spatial analysis
	\item \href{http://www.erdas.com/products/ERDASIMAGINE/ERDASIMAGINE/Details.aspx}{Erdas Imagine}: imagery processing and classification
	\item \href{http://www.filewatcher.com/b/ftp/ftp.dfd.dlr.de/pub/WASI.0.0.html}{WASI Water Color Simulator}, for modelling optical water properties under changing environment
	\item \href{http://welcome.hp.com/country/us/en/prodserv/handheld.html}{iPAQ} and GPS for data capture during the fieldwork
	\item \href{http://www.bibtex.org/de/}{BibTeX}, for management of bibliography and reference database
	\item \href{http://www.latex-project.org/}{\LaTeX}, for document typesetting, formatting and performing pdf output
	\item \href{http://www.python.org/}{Python language}, for writing auxiliary scripts (e.g. raw data interpolation)
	\item \href{http://www.gnuplot.info/}{Gnuplot} for plotting graphs
	\item \href{http://www.openoffice.org/}{Open Office} : document typesetting, data preprocessing and preliminary statistical evalution
	\item \href{http://calc2latex.sourceforge.net/}{Calc2LaTeX} : converting spreadsheets into \LaTeX environment
	\item \href{http://www.spss.com/}{SPSS (PASW Statistics 18)} : statistical data edition and analysis 
	\item \href{http://gretl.sourceforge.net/}{Gretl: Gnu Regression, Econometrics and Time-series Library} for statistic analysis
	\item \href{http://staruml.sourceforge.net/en/}{StarUML} , \href{http://live.gnome.org/Dia}{Dia} , \href{http://argouml.tigris.org/}{ArgoUML}: diagramming flowcharts for work algorithms
	\item \href{http://inkscape.org/}{Inkscape}: drawing
\end{itemize}
\pagebreak

@@

\begin{figure}[h]
	\centering
	\includegraphics[scale=0.48]{UML_ClassDiagram.jpg}
	\caption{General methodological approach for the analysis of spectral signatures. \href{http://argouml.tigris.org/}{ArgoUML}}
	\label{fig:16}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[scale=0.5]{UML_GIS.png}
	\caption{General methodological research approach. \href{http://inkscape.org/}{Inkscape}}
	\label{fig:16}
\end{figure}

@@

\begin{table}
\rowcolors{1}{Khaki}{LightYellow}
\caption{Statistical analysis of the measurements of spectral reflectance of P.oceanica (fragment)}
\centering
  \begin{tabular}{| c | c | c | c | c |}
    \hline
   	 \textbf{Statistical values} & \textbf{318.19} & \textbf{418.3448} & \textbf{518.8361} & \textbf{619.3662} \\ \hline \hline
	    Mean & 0.034521 & 0.049235 & 0.076088 & 0.085287 \\ \hline
	    St Dev & 0.019849 & 0.030338 & 0.042587 & 0.046569 \\ \hline
	   Median & 0.033035 & 0.046197 & 0.07704 & 0.080277 \\ \hline
	   Q1 & 0.019293 & 0.023706 & 0.045606& 0.049468 \\ \hline
	   Q3 & 0.042477 & 0.057934 & 0.092289 & 0.114191 \\ \hline
	   Minimum & 0.007898 & 0.010087 & 0.021373 & 0.022691 \\ \hline
	   Maximum & 0.076835 & 0.110906 & 0.18938 & 0.216231 \\ \hline
	   25th Pct & 0.019293 & 0.023706 & 0.045606 & 0.049468 \\ \hline
	   50th Pct & 0.013743 & 0.022491 & 0.031435 & 0.030808 \\ \hline
	   75th Pct & 0.009441 & -0.01174 & -0.01525 & -0.03391 \\ \hline
	   Min & 0.011395 & 0.013618 & 0.024232 & 0.026777 \\ \hline
	   Max & 0.034358 & 0.052972 & 0.097091 & 0.1 \\ \hline
  \end{tabular}
   \label{tab:4}
\end{table}
